### 2018-03-16 manuscript.rmd
updated palpons section

Palpons are typically defined as modified reduced gastrozooids [@mackie1987siphonophore]. Across different species and clades, palpons vary in their function, morphology, and location in the colony. In many species palpons are thought to play a role in digestion and circulation of the gastrovascular fluid, while other species may use them for defense (e.g _Physophora_) or sensory functions [@totton1965synopsis]. Palpons are subcategorised based on their location - palpons that are associated with gonodendra are termed gonopalpons (typically with a reduced tentacle); palpons found along the stem of the siphosome are termed palpons (typically have a tentacle, called a palpacle); and palpons found along the stem of the nectosome are termed nectosomal palpons (as in _Apolemia_) [@totton1965synopsis;@siebert2013re]. It is not clear how structure and function differs among different palpon subtypes, and a detailed histological investigation of the palpons found at different locations within species is needed. For this reason, here we only assess the presence or absence of palpons as a category, without assessing subtypes of palpons. This presumes that palpons located at different regions in the colony are derived from other palpons rather than each arising de novo by independent modification of gastrozooids, a hypothesis that itself could be challenged upon closer histological examination of palpon diversity.

>>>>

Palpons are typically defined as modified reduced gastrozooids [@mackie1987siphonophore]. In many species palpons are thought to play a role in digestion and circulation of the gastrovascular fluid, while other species may use them for defense (e.g _Physophora_) or sensory functions [@totton1965synopsis]. Palpons are subcategorised based on their location - palpons that are associated with gonodendra are termed gonopalpons (typically with a reduced tentacle); palpons found along the stem of the siphosome are termed palpons (typically have a tentacle, called a palpacle); and palpons found along the stem of the nectosome are termed nectosomal palpons (as in _Apolemia_) [@totton1965synopsis;@siebert2013re]. It is not clear how structure and function differs among different palpon subtypes, and a detailed histological investigation of palpons found at different locations within species is needed. For this reason, here we only assess the presence or absence of palpons as a category, without assessing subtypes of palpons. This presumes that palpons located at different regions in the colony are derived from other palpons rather than each arising de novo by independent modification of gastrozooids, a hypothesis that itself could be challenged upon closer histological examination of palpon diversity.
